A Motion Capture and Imitation Learning-Based Approach to Robot Control

### 2022-06-19 tex-arxiv/article.tex
start writing intro

\begin{abstract}
	Imitation Learning is a discipline of Machine Learning primarily concerned with replicating the behaviour of agents that are known to solve a particular task or family of tasks in a demonstration data set. In an industrial robotics context this presents the opportunity to replace explicit programming of behaviour with demonstrations of the task to be performed. Motion capture is one of the methods with which such demonstrations can be collected. It offers lesser model complexity compared to more indirect observation modalities such as visual data, yet requires additional data pre-processing if signals beyond effector position and orientation are relevant to the task at hand. In this paper, an approach for motion capture-based imitation learning and implicit control signal estimation is introduced and evaluated on an object throwing task.
\end{abstract}

@@

asfasgf asg agasg asgasg 
a

>>>>

\begin{abstract}
	Imitation Learning is a discipline of Machine Learning primarily concerned with replicating observed behavior of agents known to perform well on a given task, collected in demonstration data sets. In an industrial robotics context this presents the opportunity to replace explicit programming of behavior with demonstrations of the task to be performed. Motion capture is one of the methods for recording such data. It enables lesser model complexity compared to more indirect observation modalities such as visual data, yet requires additional data pre-processing if signals beyond a time series of effector positions and orientations are relevant to the task at hand. In this paper, an approach for motion capture-based imitation learning and implicit control signal estimation is introduced and evaluated on an object throwing task.
\end{abstract}

@@

Manipulator arms and other types of robots have become ubiquitous in modern industry and their use has been proliferating for decades, yet even now the primary method for programming these devices remains procedural code, hand-crafted by specially trained technicians and engineers. This significantly increases the cost and complexity of commissioning process nodes that utilize industrial robots. Therefore, it is not surprising that attempts to reduce the skill requirements and complexity of robot programming stretch back decades -- with Imitation Learning, or, as it has been otherwise referred to, Programming by Demonstration, having been proposed and reexamined many times in various technical implementations \citep{muench1994robot,attia2018global}

In statistical terms, the primary advantage of Imitation Learning based methods over related approaches such as Reinforcement Learning
